doe-pkgs-analysis

### 2021-09-06 analysis/doe-pkgs-analysis.Rmd
Added explanation of packages interconnection.

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(yaml)
library(reshape)
library(tidyverse)
library(lubridate)
library(splitstackshape)
library(igraph)
library(geomnet)
library(ggnetwork)
library(tidygraph)
library(ggraph)
```

@@

#tidy the data frame
pkg_tidy <- pkg_df %>%
  pivot_wider(names_from = L3,
              values_from = value)

@@

# create function to extract the depends, imports, and suggests 
get_pkg <- function(var){
  # select only the package name and depends/imports/suggests
  tmp_df <- pkg_tidy %>%
    select(L2, var) %>%
    # separate every depends/imports/suggests
    cSplit(var, sep = " ,")

  df <- tmp_df %>%
    pivot_longer(c(2:ncol(tmp_df)), names_to = "type", values_to = "pkg") %>%
    filter(!is.na(pkg)) %>%
    # check if the depends/imports/suggests is also a DoE package (is in list_pkg)
    mutate(doe_pkg_related = ifelse(pkg %in% list_pkg, "yes", "no")) %>%
    # filter only package whose depends/imports/suggests is a DoE
    filter(doe_pkg_related == "yes") %>%
    # tidy the data to only have the type: depends/imports/suggests
    cSplit("type", sep = "_") %>%
    select(-type_2) %>%
    rename(type = type_1)

@@

# bind data frames
pkg_edges <- rbind(depend_df, import_df, suggest_df) %>%
  select(-doe_pkg_related)

@@

# create nodes from the two previous dataframe
pkg_nodes <- full_join(from, to, by = c("L2" = "pkg"))

pkg_nodes_full <- pkg_tidy %>%
  select(L2)

@@

```{r}
ggraph(routes_tidy, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(1, 'mm')), 
                 end_cap = circle(1, 'mm')) + 
  geom_node_point() + 
  geom_node_text(aes(label = name), repel = TRUE, size = 2) +
  theme_graph()
```

@@

>>>>

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(yaml)
library(reshape)
library(tidyverse)
library(lubridate)
library(splitstackshape)
library(igraph)
library(geomnet)
library(ggnetwork)
library(tidygraph)
library(ggraph)
library(networkD3)
library(plotly)
library(qdapRegex)
```

@@

#tidy the data frame
pkg_tidy <- pkg_df %>%
  pivot_wider(names_from = L3,
              values_from = value) %>%
  mutate(author_ulrike = as.factor(ifelse(str_detect(author, "Ulrike"), 1, 0)))

@@

# create function to extract the depends, imports, and suggests 
get_pkg <- function(var){
  # select only the package name and depends/imports/suggests
  tmp_df <- pkg_tidy %>%
    select(L2, author_ulrike, var) %>%
    # separate every depends/imports/suggests
    cSplit(var, sep = " ,")

  df <- tmp_df %>%
    pivot_longer(c(3:ncol(tmp_df)), names_to = "type", values_to = "pkg") %>%
    filter(!is.na(pkg)) %>%
    # check if the depends/imports/suggests is also a DoE package (is in list_pkg)
    mutate(doe_pkg_related = ifelse(pkg %in% list_pkg, "yes", "no")) %>%
    # filter only package whose depends/imports/suggests is a DoE
    filter(doe_pkg_related == "yes") %>%
    # tidy the data to only have the type: depends/imports/suggests
    cSplit("type", sep = "_") %>%
    select(-type_2) %>%
    rename(type = type_1)

@@

# bind data frames
pkg_edges <- rbind(depend_df, import_df, suggest_df) %>%
  select(-doe_pkg_related) %>%
  select(pkg, L2, type, author_ulrike)

@@

# create nodes from the two previous dataframe
pkg_nodes <- full_join(from, to, by = c("L2" = "pkg")) %>%
  left_join(pkg_tidy, by = "L2") %>%
  select(L2, author_ulrike)

pkg_nodes_full <- pkg_tidy%>%
  select(L2)

@@

```{r}
ggraph(routes_tidy, layout = "stress") + 
  geom_edge_link(aes(color = type),
                 arrow = arrow(length = unit(1, 'mm')), 
                 end_cap = circle(1, 'mm')) + 
  geom_node_point(aes(color = author_ulrike)) + 
  scale_color_manual(values = c("#707B7C", "#F5B041"), labels = c("no", "yes")) +
  geom_node_text(aes(label = name), repel = TRUE, size = 2) +
  theme_graph()

```

@@

Next:
1. Color the nodes based on author (Binary variable whether the pkg is authored by Ulrike or not)
2. Using interactive graph with D3
3. Write on the paper

# Interactive Plot

```{r}
nodes_d3 <- pkg_nodes %>%
  rowid_to_column("id") %>%
  mutate(id = id - 1)

edges_d3 <-routes_tidy %>%
  activate(edges) %>%
  data.frame() %>%
  mutate(from = from - 1,
         to = to - 1)

forceNetwork(Links = edges_d3, Nodes = nodes_d3, Source = "from", Target = "to", 
             NodeID = "L2", Group = "author_ulrike", 
             opacity = 1, fontSize = 16, zoom = TRUE)
```
